---
title: "550 Project"
author: "Xiuran Lin"
date: "`r Sys.Date()`"
output: html_document
---
# **Introduction**
## My dataset is about stroke prediction. According to the World Health Organization (WHO) stroke is the 2nd leading cause of death globally, responsible for approximately 11% of total deaths. I am going to summarize the data with some descriptive analysis including tables and figures to show the possible difference or correlation from the data.

# **Attribute Information**
## 1) id: unique identifier
## 2) gender: "Male", "Female" or "Other"
## 3) age: age of the patient
## 4) hypertension: 0 if the patient doesn't have hypertension, 1 if the patient has hypertension
## 5) heart_disease: 0 if the patient doesn't have any heart diseases, 1 if the patient has a heart disease
## 6) ever_married: "No" or "Yes"
## 7) work_type: "children", "Govt_jov", "Never_worked", "Private" or "Self-employed"
## 8) Residence_type: "Rural" or "Urban"
## 9) avg_glucose_level: average glucose level in blood
## 10) bmi: body mass index
## 11) smoking_status: "formerly smoked", "never smoked", "smokes" or "Unknown"*
## 12) stroke: 1 if the patient had a stroke or 0 if not
## *Note: "Unknown" in smoking_status means that the information is unavailable for this patient

```{r, set-chunk-opts, echo = FALSE, eval = TRUE, warning=FALSE, message=FALSE}
library(knitr)
library(here)
library(dplyr)
library(tidyverse)
opts_chunk$set(
  echo = TRUE, warning = FALSE, message = FALSE
)
```
# **Read data set**

```{r, load-data, message=FALSE}
here::i_am("550_project_report_Xiuran_Lin.Rmd")
 data <- readRDS(
   file = here::here("output/data_clean.rds")
 )

```
# **Table**
#### This table showed BMI level and average glucose level for different work type among study participants.
```{r, table1}
library(gtsummary)

table_one <- readRDS(
  file = here::here("output/table_one.rds")
)
table_one
```


# **Graph Analysis**
#### This is the mosaic plot to show the difference of bmi level between people who have married and people who have not married.
```{r figure, fig.width=10, fig.height=8}
library(ggplot2)

knitr::include_graphics(
  here::here("output/mosaicplot.png")
)
```